%CV William Le Ferrand
\documentclass{cv}

\usepackage[francais]{babel}
\usepackage[paper=a4paper,textwidth=170mm, margin=20mm]{geometry}
\usepackage{hyperref}
\newcommand{\lieu}[1]{}
\newcommand{\activite}[1]{\textbf{#1}\ }
\newcommand{\comment}[1]{\textsl{#1}\ }



\begin{document}

\begin{chapeau}
\begin{adresse}
	William Le Ferrand\\%
	5, place du President Wilson\\%
	31000 Toulouse\\%
        France\\%
	\ligne\\%
	%\raggedright
        +33 6 33 92 44 18\\%
	\texttt{william.le-ferrand@m4x.org}
\end{adresse}
\begin{etatcivil}
  \texttt{linkedin: williamleferrand}\\%
  \ligne\\%
  Born 1987\\
  French Citizen,\\
  Married, 3 children
\end{etatcivil}
\end{chapeau}

\vspace{4mm}
\begin{center}
Transforming industrial & tech organizations by building product-driven, high-performance teams that deliver measurable results
\end{center}
\vspace{2mm}

	%%%%%%%%%%%%%%%%%%
	% Bloc rubriques %
	%%%%%%%%%%%%%%%%%%


\begin{rubriquetableau}[4.0cm]{Activity}

2024 & \activite{sogeclair.com}
   \comment{designed and implemented a digital transformation plan for a global group spanning 19 entities and 1,200 employees.}  \\[5mm]

2022 - 2023 & \activite{wyca.fr}
   \comment{hired to reboot a 7 years old startup. rebuilt a team of 10 engineers and a product-centric culture, moved the company from building PoCs to selling autonomous mobile robots with a crisp ROI. failed at raising additional funds }  \\[7mm]

2020 - 2022
& \activite{lantern.so}
   \comment{automatic insight generation on product data. YC-funded, engineer \#1,
  responsible for the ingestion and data processing
  infrastructure}  \\[5mm]
  
 2019 - 2022 & \activite{hivyleague.com}
   \comment{distributed apiaries on airfields, managed via an iPhone
     app leveraging custom hardware and ELK-based dashboards. building hardware
     dedicated to managing the varroa mite in honeybees colonies}  \\[5mm]

2016 - 2020
& \activite{logichub.com}
   \comment{detection, classification and prevention of security
     breaches at scale. working with
     US (both coasts) \& India teams, building the data processing
     pipeline and managing its deployment on-premises} \\[9mm]

2013 - 2016
& \activite{sumologic.com}
   \comment{designed and implemented a real time log ingest and search
     component that handles 5Tb+/day. designed and implemented a
     metrics collection and storage platform handling 2M dps from Kafka
   to Cassandra, deployed in AWS} \\ 
   
2011 - 2013 & \activite{besport.com} \comment{cofounded a sport social
  network, hired a team of 9 engineers, raised 1.2m\$. company
  relocated in Paris, still active} \\[5mm]
  
 2010 - 2011 & \activite{hypios.com} \comment{dealt with all the engineering aspects of building an open-innovation platform that connects researchers with companies} \\[5mm]

2010 & \activite{corefarm.com} \comment{built 3d rendering farm for
  Blender 3D in AWS while attending school. Reached 100 users, commercial failure, open-sourced}



\end{rubriquetableau}

\begin{rubriquetableau}[4.0cm]{Academics}


  2019 - 2020
	& \activite{Cornell University}
	\comment{Master Beekeeper Program (missed the practical exam because of covid travel restrictions)} \\[1mm]

2006 - 2010
	& \activite{Ecole Polytechnique}
	\comment{Master in Computer Science}

 \end{rubriquetableau}

\begin{rubrique}{Other qualifications}
\begin{itemize}
\item FAA CMEL/IR, EASA PPL, French Classe 6, 1 Blue Spruce, 900 hours TT
\end{itemize}
\end{rubrique}

\end{document}
